How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-06 tse-paper/content.tex
Add new table. Improve existing figures.

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/techniques.pdf}
		\caption{Frequency of different technique labels for
		labels $>1$ occurence.}
		\label{fig:litsur:techniques}
\end{figure}

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/info_target.pdf}
		\caption{Frequency of different targeted information
		labels for
		labels $>1$ occurence.}
		\label{fig:litsur:info_target}
\end{figure}

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/use.pdf}
		\caption{Frequency of different usage of output labels for
		labels $>1$ occurence.}
		\label{fig:litsur:use}
\end{figure}

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/log_producer.pdf}
		\caption{Frequency of different log producer labels for
		labels $>1$ occurence.}
		\label{fig:litsur:log_producer}
\end{figure}

@@

\begin{table*}[]
\centering
\caption{Overview of the described chunk retrieval techniques.}
\begin{tabularx}{\textwidth}{@{}XlXlXX@{}}
\toprule
Name			     & Acronym & Identification Technique
& Granularity & Configuration & Source		  \\
\midrule
Program Synthesis by Example & PBE     & Regular expression program
& Character   & In/output examples	\\
Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
expected number of lines & Line        & Output examples	   \\
Keyword Search		     & KWS     & Keywords, expected number of
lines			 & Line        & Keywords, context length  \\
Random Line Retrieval	     & RLR     & Random sample
& Line	      & Retrieval length	  \\
Diff Approach		     & ---     & Line not present in successful
log, information retrieval  & Line	  & Logs from failing and
successful builds      \\
\bottomrule
\end{tabularx}
\label{tab:ctr}
\end{table*}

>>>>

\begin{table*}[]
\centering
\caption{Overview of buildlog analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXX@{}}
\toprule
Name			     & Source(s)	& Frequency 	  \\
\midrule
Parser  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}	\\
Regular expression  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}	\\
Manual inspection  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}	\\
Machine Learning  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}	\\
Natural Language Processing  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}	\\
Information Retrieval  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}	\\
Analysis  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}	\\
Keyword Search  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}	\\
Scan  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}	\\
Other  & & \includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}	\\
\bottomrule
\end{tabularx}
\label{tab:obat}
\end{table*}

\begin{figure}[tbhp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/info_target.pdf}
		\caption{Information targeted in build log analysis.}
		\label{fig:litsur:info_target}
\end{figure}

\begin{figure}[tbhp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/use.pdf}
		\caption{Purpose of build log analysis.}
		\label{fig:litsur:use}
\end{figure}

\begin{figure}[tbhp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/log_producer_long-cropped.pdf}
		\caption{Frequency of supported log producer.}
		\label{fig:litsur:log_producer}
\end{figure}

@@

\begin{table*}[]
\centering
\caption{Chunk retrieval techniques.}
\begin{tabularx}{\textwidth}{@{}XlXlXX@{}}
\toprule
Name			     & Acronym & Identification Technique
& Granularity & Configuration & Source		  \\
\midrule
Program Synthesis by Example & PBE     & Regular expression program
& Character   & In/output examples	\\
Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
expected number of lines & Line        & Output examples	   \\
Keyword Search		     & KWS     & Keywords, expected number of
lines			 & Line        & Keywords, context length  \\
Random Line Retrieval	     & RLR     & Random sample
& Line	      & Retrieval length	  \\
Diff Approach		     & ---     & Line not present in successful
log, information retrieval  & Line	  & Logs from failing and
successful builds      \\
\bottomrule
\end{tabularx}
\label{tab:ctr}
\end{table*}
